MCC Models

### 2019-03-12 papers/full_paper/models.Rmd
refactor param passing for ex3

```{r model setup ex 3 adults}
# create datafiles with model parameters
model_params_ex3 <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  speak_opt = adult_model_param$so_map)
prior_pref_summary <- adult_ex2_preference_data %>%
  group_by(condition)
prior_pref_same <- adult_ex2_preference_data %>%
  filter(condition == "same_speaker")%>%
  summarise(prior = mean(correct))

prior_pref_diff <- adult_ex2_preference_data %>%
  filter(condition == "different_speaker")%>%
  summarise(prior = mean(correct))

prior_novel_same <- adult_ex2_novelty_data %>%
  filter(condition == "same_speaker")%>%
  summarise(prior = mean(correct))

prior_novel_diff <- adult_ex2_novelty_data %>%
  filter(condition == "different_speaker")%>%
  summarise(prior = mean(correct))

makePriorList = function(p){
  c(1 - p, 1 - p, p)
}

makeInversePriorList = function(p){
  c(p, p, 1 - p)
}

model_params_ex3$prior = list(
  makePriorList(prior_pref_same$prior), 
  makeInversePriorList(prior_pref_same$prior), 
  makePriorList(prior_pref_diff$prior), 
  makeInversePriorList(prior_pref_diff$prior), 
  makePriorList(prior_novel_same$prior), 
  makeInversePriorList(prior_novel_same$prior), 
  makePriorList(prior_novel_diff$prior), 
  makeInversePriorList(prior_novel_diff$prior)
)
```

@@

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.prior,row.speak_opt)

@@

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: row.prior}));
      return obj.shape == "circle" ? 1 : 0
  }})

@@

@@

>>>>

```{r model setup ex 3 adults}
# create datafiles with model parameters
model_params_ex3 <- expand.grid(
  common_ground_manipulation = c("preference", "novelty"),
  speaker = c("same_speaker", "different_speaker"),
  speak_opt = adult_model_param$so_map
  )

prior_pref_summary <- bind_rows(
  adult_ex2_preference_data,
  adult_ex2_novelty_data) %>%
  group_by(condition, experiment) %>%
  summarise(prior = mean(correct)) %>%
  mutate(experiment = gsub("adult_ex2_", "", experiment)) %>%
  rename(common_ground_manipulation = experiment,
         speaker = condition)

model_params_ex3 <- left_join( 
  model_params_ex3, 
  prior_pref_summary, by = c("common_ground_manipulation", "speaker")
) %>%
  rename(congruent = prior) %>%
  mutate(incongruent = 1 - congruent) %>%
  gather(alignment, prior, congruent, incongruent)

@@

var output = map(function(row){
    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)

@@

var output = map(function(row){
  var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]

@@

var priorProbLst = [.5, .5, .5]

@@

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)
